% !TEX root = ../thesis_main.tex


% Acknowledgements
\clearpage
\begin{acknowledgement}
I have greatly enjoyed my time working with the TRINAT collaboration, and I am indebted to its present and former members for building up much of the infrastructure that was used in this project.  John Behr in particular has worked tirelessly to manage and improve the experimental setup while still making himself available for discussions on physics.  Over the years I've worked with him, he has always been reliably available to help out when I was confused or when something went wrong, and I am grateful to have had the opportunity to work with him.  Dan Melconian's focus and insight have also been invaluable to me during this project; I surely would have spent much more time confused both about physics and about how to approach certain problems had he not been involved.  

I've also learned a great deal from the time spent working with Ben Fenker and Spencer Behling, both of whom have made major contributions to the TRINAT laboratory and software infrastructure that is foundational to this project.  It has been a pleasure working with them both.  I have also enjoyed the opportunity to work with James McNeil, Alexandre Gorelov, and the late Danny Ashery --- each of whom has made valuable contributions to this project and to the collaboration in general.  

Finally, Gerald Gwinner has been remarkably adept at steering me successfully through the variety of administrative hurdles encountered during my time as a Ph.D. student; I would not have gotten nearly as far without his help, and I am grateful to have had the opportunity to work with him.  

%
%And Susan Beshta.
\end{acknowledgement}
